\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
Final Abstract and Title
section 2

\section{A Vocabulary to Describe RDF Constraints Generically} 
\label{sec:vocabulary}

Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.

>>>>

\section{A Vocabulary to Describe RDF Constraints of any RDF Constraint Type} 
\label{sec:vocabulary}

Prerequisites to develop a vocabulary to describe RDF constraints of any RDF constraint type are (1) to specify the underlying semantics for RDF validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on RDF validation.
